Supplementary Information

### 2020-08-31 doc/manuscript/MEE_manuscript_SI.Rmd
updated fig captions

![**Figure S5 | Best GLS models for Barro Colorado Island (Panama) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/BCI.png){ width=78% }

@@

![**Figure S6 | Best GLS models for Huai Kha Khaeng (Thailand) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/HKK.png){ width=78% }

@@

![**Figure S7 | Best GLS models for Little Tesuque  (New Mexico, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/NewMexico.png){ width=78% }

@@

[**Figure S8 | Best GLS models for Cedar Breaks  (Utah, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.]

@@

![**Figure S9 | Best GLS models for SCBI (Virginia, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/SCBI.png){ width=78% }

@@

![**Figure S10 | Best GLS models for Lilly Dickey Woods (Indiana, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/LillyDickey.png){ width=78% }

@@

![**Figure S11 | Best GLS models for Harvard Forest (Massachusetts, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/HarvardForest.png){ width=78% }

@@

![**Figure S13 | Best GLS models for Zofin (Czech Republic) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/Zofin.png){ width=78% }

@@

![**Figure S14 | Best GLS models for Scotty Creek (NW Territories, Canada) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin*. For each species, relationships are plotted if included in top model, with dashed lines indicating terms that do not significantly improve the model (relative to a model without). Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/ScottyCreek.png){ width=78% }

>>>>

![**Figure S5 | Best GLS models for Barro Colorado Island (Panama) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/BCI.png){ width=75% }

@@

![**Figure S6 | Best GLS models for Huai Kha Khaeng (Thailand) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/HKK.png){ width=75% }

@@

![**Figure S7 | Best GLS models for Little Tesuque  (New Mexico, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/NewMexico.png){ width=75% }

@@

[**Figure S8 | Best GLS models for Cedar Breaks  (Utah, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.]

@@

![**Figure S9 | Best GLS models for SCBI (Virginia, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/SCBI.png){ width=75% }

@@

![**Figure S10 | Best GLS models for Lilly Dickey Woods (Indiana, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/LillyDickey.png){ width=75% }

@@

![**Figure S11 | Best GLS models for Harvard Forest (Massachusetts, USA) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/HarvardForest.png){ width=75% }

@@

![**Figure S13 | Best GLS models for Zofin (Czech Republic) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/Zofin.png){ width=75% }

@@

![**Figure S14 | Best GLS models for Scotty Creek (NW Territories, Canada) for all three growth metrics: $\Delta r$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/ScottyCreek.png){ width=75% }
